---
title: "Code to generate the figures for Access regimes and fishers' stewardship"
author: "Ignacia Rivera"
date: "Sep 27, 2018"
output: pdf_document 
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(plyr)
library(here)
library(tidyverse)
library(foreign)
```

## Metadata 

1) union: unique id for each union (not diclosed to ensure anonimity)
 
2) performance: type of association 

- High performance =1
- Low performance =2 

3) framing: framing under which the game was played

- Loco = 1 
- Hake = 2 

4) id: unique identifier for each fisher

5) round: round of the game

- From 1 to 20

6) overextraction: number of units overharvested by a subject in a given round
- From 0 to 50

7) observer: the role assigned to that subject in that round 

- Observer = 1
- Inactive = -1
- Inspected = 0
- Round with no observation = NA

8) overext_observed: overextraction performed by the subject being inspected by the subject 

- From 0 to 50
- Round with no observation = NA

9) report: whether the subject reported a parnter's violation when having the chance

- Yes = 1
- No = 0
- Round with no obsrevation = NA

10) punished: whether the subject got punished after being observed violating the quota 

- Yes = 1
- No = 0
- Round with no obsrevation = NA

11) round_profit: profit made by the subject in a given round

- From 0 to 1,500

12) group_id: unique number for group identification


```{r raw experiment data, echo = FALSE, message=FALSE, warning=FALSE, include=FALSE}

DB <- read_csv(here::here('Data/DB_fishers.csv'), col_names = T) 


# Generating variables

DB <- DB %>% 
  mutate(compliance = ((50 - overextraction) * 100)/50, # individual percent of compliance in each round
         round_adj = ifelse(round >= 11, round - 11, round - 1), # adjusting rounds for linear models 
         stage = ifelse(round < 11 , 1, 2), # generating dicotomic variable for stage
         frame = ifelse(framing ==1, 'Loco', 'Hake'), # generating character variable for frame
         frame = factor(frame, levels = c('Hake', 'Loco')), # sorting names of frames
         Loco = ifelse(framing ==1, 1, 0),  # generating dummy variable for frame loco
         Hake = ifelse(framing ==2, 1, 0), # generating dummy variable for frame hake
         performance_name = ifelse(performance == 1, 'High performance', 'Low performance')) 

DB_group <- DB %>% 
  group_by(group_id, frame, round, performance) %>% 
  summarize(mean_group_compliance = mean(compliance)) %>%  
  ungroup() %>% 
  group_by(performance, frame, round) %>% 
  summarise(mean_compliance = mean(mean_group_compliance), error = qnorm(0.975)*sd(mean_group_compliance)/sqrt(length(mean_group_compliance)), std.error = sd(mean_group_compliance)/sqrt(length(mean_group_compliance))) %>% 
  ungroup() %>% 
  mutate(ci_low = mean_compliance - error, 
         ci_high = mean_compliance + error,
         association = ifelse(performance == 1, 'High-performance associations', 'Low-performance associations'), 
         stage = ifelse(round < 11, 'Non-enforced', 'Peer-enforced')) 


```

### Figure 1. Compliance evolution

```{r plot complaince evolution, echo = FALSE, message=FALSE, warning=FALSE}

#pdf(file = "Figure_1.pdf",   
#    width = 6.5, 
#    height = 4.5)

plot_compliance <- ggplot(DB_group, aes(x= round, y=mean_compliance)) + 
  geom_point(aes(col = frame), size = 1.3) +
  geom_line(aes(col=frame), size = .67)+
  #geom_errorbar(aes(ymin=mean_compliance - std.error, ymax= mean_compliance + std.error, col = frame)) +
  geom_ribbon(aes(ymin=mean_compliance - error, ymax= mean_compliance + error, col = NA, fill = frame), alpha = .15, show.legend = FALSE) +
  scale_color_manual(values = c("red1", "royalblue3"), labels = c("pseudo OA (Hake)", "CEAR (Loco)"))+
  scale_fill_manual(values = c("red1", "royalblue3"), labels = c("pseudo OA (Hake)", "CEAR (Loco)"))+
  theme_bw() + 
  xlab(expression(bold("Round"))) +
  ylab(expression(bold("Compliance (%)")))+
  scale_x_continuous(expand = c(0,0), breaks=c(seq(1,20,1)), labels = c(seq(0,9,1), seq(0,9,1)))+
  scale_y_continuous(limits = c(0,100), breaks = c(seq(0,100,20)), expand = c(0,0))+
  geom_vline(xintercept=10.5, size=5.4, col= 'white')+
  facet_wrap(~association, strip.position = "top")+
  theme(legend.position="bottom", legend.title=element_blank(), legend.text =    element_text(size=11), panel.grid = element_blank(), plot.title = element_text(hjust = 0.5), panel.grid.major = element_blank(), panel.grid.minor = element_blank())+
  theme(panel.grid.major = element_blank(),
        panel.grid.minor = element_blank(),
        strip.background = element_blank(),
        strip.text = element_text(size= 11, face = "bold", hjust = 0, vjust = 3),
        panel.border = element_rect(colour = "dark grey"), 
        panel.spacing.x=unit(1, "lines"), 
        axis.title.x = element_text(margin = margin(t = 10, r = 0, b = 0, l = 0)), 
        axis.title = element_text(size = 11), 
        axis.text = element_text(size = 8))

plot_compliance

#ggsave(
#  "Figure_1_rev.pdf",
#  plot = plot_compliance,
#  device = "pdf",
#  path = here::here("Figures_and_tables"),
#  scale = 1,
#  width = 16,
#  height = 10,
#  units = "cm",
#  dpi = 600,
#  limitsize = TRUE
#)

```

## Figure 2. Probability of report

```{r plot report, echo = FALSE, message=FALSE, warning=FALSE}

# generating data frame for probability of report 

DB_report <- DB %>% 
  filter(overext_observed > 0 & observer==1) %>% # only observers (i.e. inspectors) who observed overharvest above zero had the opportunity to report
  group_by(framing, performance, group_id) %>% 
  summarise(
    report_oportunities = n(),
    report_counts= sum(report)) %>% 
  ungroup() %>% 
    mutate(probability = (report_counts)/report_oportunities) %>% 
  group_by(framing, performance) %>% 
  summarise(mean_prob= mean(probability), error = qnorm(0.975)*sd(probability)/sqrt(length(probability))) %>% 
  mutate(ci_low = mean_prob, ci_low = mean_prob - error, ci_up= mean_prob + error)

#pdf(file = "Figure_2.pdf",   
#    width = 4.2, 
#    height = 5.5)

# Plot report
plot_report <- ggplot(DB_report, aes(x=as.factor(performance), y=mean_prob, fill=as.factor(framing))) + 
  geom_bar(stat='identity', width=0.5, position=position_dodge(0.6))+
  geom_errorbar(aes(x=as.factor(performance), ymin = ci_low, ymax= ci_up), width=0.25, position=position_dodge(0.6), size = 0.4)+
  scale_fill_manual(values = c("royalblue3", "red1"), labels = c("CEAR (Loco)", "pseudo OA (Hake)"))+
  xlab(expression(bold("Association type")))+
  ylab(expression(bold("Probability of reporting")))+
  scale_y_continuous(expand = c(0, 0), limits=c(0,1), breaks=seq(0,1, by=0.2))+
  scale_x_discrete(labels=c("1" = "High-performance", "2" = "Low-performance"))+ 
  theme_bw()+
  theme(legend.position="bottom", legend.title=element_blank(), legend.text = element_text(size=10, margin = margin(t= 10, r= 0, b =0, l =0)), 
        panel.grid = element_blank(), 
        strip.text = element_text(size=11), 
        axis.title = element_text(size = 12), 
        axis.text = element_text(size = 11), 
        axis.title.y = element_text(margin = margin(t = 0, r = 10, b = 0, l = 0)), 
        axis.title.x = element_text(margin = margin(t = 10, r = 0, b = 0, l = 0)))

plot_report

#ggsave(
#  "Figure_2_rev.pdf",
#  plot = plot_report,
#  device = "pdf",
#  path = here::here("Figures_and_tables"),
#  scale = 1,
#  width = 11,
#  height = 14,
#  units = "cm",
#  dpi = 600,
#  limitsize = TRUE
#)
```



