---
title: Effects of experience with access regimes on stewardship behaviors of small-scale fishers
author: "Ignacia Rivera"
output: 
  html_document:
      code_folding: hide
      theme: cosmo
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(gt)
library(here)
library(tidyverse)
library(stargazer)
library(knitr)
library(nlme)
library(lme4)
library(sandwich)
library(gtable)
library(grid)

#turninf off scientific notation

options(scipen = 999)
```

# Data analysis and figures {.tabset}

## **1. Data description**

1) **union:** unique id for each union (not disclosed to ensure anonymity)
 
2) **performance:** type of association 

- High performance = 1
- Low performance = 2 

3) **framing:** framing under which the game was played

- Loco = 1 
- Hake = 2 

4) **id:** unique number for subject identification built combining codes for id, union and frame

5) **group_id:** unique number for group identification built combining codes for union, session and frame (note that groups were reassembled in each round for union 3)

6) **round:** round of the game

- From 1 to 20

7) **overextraction:** number of units overharvested by a subject in a given round

- From 0 to 50

8) **observer:** the role assigned to that subject in that round 

- Observer = 1
- Inactive = -1
- Inspected = 0
- Round with no observation = NA

9) **overext_observed:** overextraction performed by the subject being inspected by the subject 

- From 0 to 50
- Round with no observation = NA

10) **report:** whether the subject reported a parnter's violation when having the chance

- Yes = 1
- No = 0
- Round with no obsrevation = NA

11) **punished:** whether the subject got punished after being observed violating the quota 

- Yes = 1
- No = 0
- Round with no obsrevation = NA

12) **round_profit:** profit made by the subject in a given round

- From 0 to 1,500

```{r importing database, echo = FALSE, message=FALSE, warning=FALSE}

db.raw <- read_csv(here::here('data/db.fishers.raw.csv'), col_names = T) %>%
  mutate(group_id = interaction(union, group, framing, sep=''),
         id = interaction(id, union, framing, sep=''),
         round = ifelse(round <= 13, round - 3, round - 6),
         overext_observed = ifelse(observer == 1, overext_observed, NA),
         report= ifelse(observer == 1, report, NA),
         punished = ifelse(observer == 0, punished, NA),
         observer = ifelse(round < 11, NA, observer)) %>% 
  select(union, 
         performance, 
         framing, 
         id, 
         group_id,
         round,
         overextraction,
         observer,
         overext_observed,
         report,
         punished,
         round_profit)

```


```{r importing data, echo = FALSE, message=FALSE, warning=FALSE}

db <- db.raw %>% 
  # group id with single group per session in union 3 to account for random matching in every round
        mutate(
          group.id.fixed = ifelse(union == 3 & framing == 1, "888", 
          ifelse(union == 3 & framing == 2, "999", as.character(group_id)))) %>% 
  # variables for analysis
  ## individual percent of compliance in each round
  mutate(compliance = ((50 - overextraction) * 100)/50, 
         ## dichotomous variable for stage
         stage = ifelse(round < 11 , 1, 2), 
         ## character variable for stage
         stage.nm = ifelse(round < 11 , "Unenforced", "Peer enforced"), 
         ## character variable for frame
         frame.nm = ifelse(framing == 1, 'Loco', 
                           ifelse(framing ==2, 'Hake', 'Money')), 
         ## sorting character variable for frame
         frame.nm = factor(frame.nm, levels = c('Hake', 'Loco', 'Money')), 
         ## character variable for performance 
         performance.nm = ifelse(performance == 1, 'High performance', 
                                 ifelse(performance == 2, 'Low performance',
                                        'Student'))) 

db.print <- head(db)
knitr::kable(db.print, col.names = gsub("[.]", " ", names(db)))
```


## **2. Differences in compliance** {.tabset}

### 2.a. Non-parametric tests for differences in individual mean compliance (Appendix S7)
```{r non-parametric comparisons of individual mean compliance, echo = FALSE, message=FALSE, warning=FALSE}

# Aggregating observations over rounds at the individual level 

db.ind.agg <- db %>% 
  group_by(frame.nm, performance.nm, stage.nm, id) %>% 
  summarise(compliance= mean(compliance)) %>% 
  select(-id) 

# Testing significant differences between frames for each association type across all rounds

frame.comp <- db.ind.agg %>%
  group_by(performance.nm) %>% 
  summarize(p.value = wilcox.test(compliance ~ frame.nm)$p.value, 
            stat = wilcox.test(compliance ~ frame.nm)$statistic) %>% 
  mutate(frame.nm = 'vs',
         stage.nm = 'All')

# Testing significant differences between association type for each frame across all rounds

performance.comp <- db.ind.agg %>%
  group_by(frame.nm) %>% 
  summarize(p.value = wilcox.test(compliance ~ performance.nm)$p.value, 
            stat = wilcox.test(compliance ~ performance.nm)$statistic) %>% 
  mutate(performance.nm = 'vs',
         stage.nm = 'All')


# Testing significant differences between stages since observations are repeated it must be a paired test

stages.comp <- db.ind.agg %>% 
  group_by(frame.nm, performance.nm) %>% 
  summarize(p.value = wilcox.test(compliance ~ stage.nm, paired = T)$p.value,
            stat = wilcox.test(compliance ~  stage.nm, paired = T)$statistic) %>% 
  mutate(stage.nm = 'vs')

# Unifying outputs

test.comp <- rbind(frame.comp, performance.comp, stages.comp) %>% 
  select(performance= performance.nm, frame = frame.nm, stage= stage.nm, p.value, stat) %>% 
  mutate(corrected.p.value = p.value * 8, 
         sign.corrected = ifelse(corrected.p.value < 0.05,"*", ""))  # Correcting for 8 hypotheses using Bonferroni

wilx.comp <- gt(test.comp) %>% 
   fmt_number(columns = vars(p.value, corrected.p.value), decimals = 3) %>% 
  tab_header(
    title = md("Wilcoxon rank-sum: differences in compliance levels")
  ) %>% 
  tab_source_note(
    source_note = md("Significance level is ajusted using a Bonferroni correction for 8 hypotheses")
  )%>% 
  tab_source_note(
    source_note = md("Tests comparing differences between stages are paired")
  )

wilx.comp
```

### 2.b. Plot of mean individual compliance per treatment and association type (Fig. 1)
```{r bar plot mean compliance, echo = FALSE, message=FALSE, warning=FALSE, fig.cap= '**Fig 1.** Mean percent compliance in the common-pool-resource game with the individual quota of loco, which is fished under collective, exclusive access (CEAR) in real life and with the individual quota of hake, which is fished under pseudo-open access (OA) in real life  for high-performance associations and low-performance associations (error bars, 95% CIs computed at the individual level; n=30).'}

# summary statistic for bar plot on individual compliance
db.summary <- db %>% 
  group_by(performance.nm, frame.nm, id) %>% 
  summarise(mean.ind.comp = mean(compliance)) %>% 
  ungroup() %>% 
  group_by(performance.nm, frame.nm) %>% 
  summarise(mean = mean(mean.ind.comp),
          sd = sd(mean.ind.comp),
          n = length(mean.ind.comp)) %>% 
  mutate(error = qnorm(0.975)*(sd/sqrt(n)), 
         ci.low = mean - error, 
         ci.high = mean + error) %>% 
  rename(
    Performance = performance.nm,
    Frame = frame.nm
  )

# plotting

bar_compliance <- ggplot(db.summary, aes(x=Performance, y= mean, fill= reorder(Frame, -mean))) + 
  geom_bar(stat='identity', width=0.5, position=position_dodge(0.6))+
  geom_errorbar(aes(x= Performance, ymin = ci.low, ymax= ci.high), width=0.25, position=position_dodge(0.6), size = 0.4)+
  scale_fill_manual(values = c("royalblue3", "red1"), labels = c("CEAR (Loco)", "pseudo-OA (Hake)"))+
  xlab(expression(bold("Association type")))+
  ylab(expression(bold("Compliance (%)")))+
  scale_y_continuous(expand = c(0, 0), limits=c(0,100), breaks=seq(0,100, by=20))+
  #facet_wrap(~Performance)+
  scale_x_discrete(labels=c("1" = "High-performance", "2" = "Low-performance"))+ 
  theme_bw()+
  theme(legend.position="top", legend.title=element_blank(), legend.text = element_text(size=10, margin = margin(t= 10, r= 0, b =0, l =0)), 
        panel.grid = element_blank(), 
        strip.text = element_text(size=11), 
        axis.title = element_text(size = 12), 
        axis.text = element_text(size = 11), 
        axis.title.y = element_text(margin = margin(t = 0, r = 8, b = 0, l = 0)), 
        axis.title.x = element_text(margin = margin(t = 8, r = 0, b = 0, l = 0)))

bar_compliance
#ggsave("Fig1_rev_rev.pdf", plot = bar_compliance, device = "jpg", path = here::here("figures"), scale = 1, width = 16, height = 12, units = "cm", dpi = 600, limitsize = TRUE)

```

### 2.c. Comparing number of subjects that choose to comply in every round between treatments within association types (Main text)
```{r analysis for subjects that choose to comply in every round, echo = FALSE, message=FALSE, warning=FALSE}

# Counting number of compliers in every round

db.compliers <- db %>% 
  group_by(frame.nm, performance.nm, id) %>% 
  summarise(compliance= mean(compliance)) %>% 
  mutate(complier = ifelse(compliance == 100, 1, 0)) %>% 
  group_by(frame.nm, performance.nm) %>% 
  summarise(n.compliers = sum(complier))

# Contingency table of compliers for high performance associations (compliers vs. non-compliers in each treatment)

table.compliers.hp <- rbind(
        #cear
        c(10,20),
        #oa
        c(2,28))

# Running fisher exact test and correcting for two hypotheses 

fisher.compliers.hp.stat <- round(fisher.test(table.compliers.hp)$estimate, 3)
fisher.compliers.hp.p <- round(fisher.test(table.compliers.hp)$p.value, 3)
fisher.compliers.hp.p.corrected <- round(fisher.test(table.compliers.hp)$p.value*2, 3)

# Contingency table of compliers for low performance associations (compliers vs. non-compliers in each treatment)

table.compliers.lp <- rbind(
        #cear
        c(2,28),
        #oa
        c(1,29))

# Running fisher exact test and correcting for two hypotheses 

fisher.compliers.lp.stat <- round(fisher.test(table.compliers.lp)$estimate, 3)
fisher.compliers.lp.p <- round(fisher.test(table.compliers.lp)$p.value, 3)
fisher.compliers.lp.p.corrected <- round(fisher.test(table.compliers.lp)$p.value*2, 3)

# unifying outcomes

fisher.compliers.test <- rbind(
        c('High performance', fisher.compliers.hp.stat, fisher.compliers.hp.p, fisher.compliers.hp.p.corrected),
        c('Low performance', fisher.compliers.lp.stat, fisher.compliers.lp.p, fisher.compliers.lp.p.corrected)) %>% 
  as.data.frame() %>% 
  rename('Performance' = 'V1',
         'p.value' = 'V3', 
         'corrected.p.value' = 'V4') %>% 
  gt() %>% 
  tab_header(
    title = md("Fisher's exact test for count data: differences in number of compliers between frames")
  ) %>% 
  tab_source_note(
    source_note = md("Significance level is ajusted using a Bonferroni correction for 2 hypotheses")
  )

fisher.compliers.test


```


### 2.d. Weighted OLS of group compliance on treatment, association type and stage variables (Appendix S8)
```{r creating db at the group level, echo = FALSE, message= FALSE, warning = FALSE}

db.group <- db %>% 
  # marking punishment opportunities 
  mutate(report.opportunity = ifelse(observer ==1 & overext_observed > 0, 1, 0)) %>% 
  # note that we are grouping by group_id_fixed to account for the rematching between rounds that occur in sessions in union 3
  group_by(frame.nm, performance.nm, stage.nm, round, group.id.fixed) %>%
  # computing outcome variables at the group level
  summarise(mean.group.com = mean(compliance),
            num.opp.reporting = sum(report.opportunity, na.rm = T),
            num.reports = sum(report, na.rm = T), 
            group.prob.report = num.reports / num.opp.reporting,
            mean.obs.overharvest = mean(overext_observed, na.rm = T)) %>%  
  # creating dummy variables and interactions 
  mutate(
    cear = ifelse(frame.nm == 'Loco', 1, 0), 
    peer.enf = ifelse(stage.nm == 'Peer enforced', 1, 0), 
    hp = ifelse(performance.nm == 'High performance', 1, 0), 
    non.enf.rounds = ifelse(round < 11, round-1,0), 
    peer.enf.rounds = ifelse(round > 10, round - 11, 0), 
    cear.peer.enf = ifelse(frame.nm == 'Loco' 
                           & stage.nm == 'Peer enforced', 1, 0), 
    cear.hp = ifelse(frame.nm == 'Loco' 
                           & performance.nm == 'High performance', 1, 0), 
    oa.hp = ifelse(frame.nm == 'Hake' 
                           & performance.nm == 'High performance', 1, 0),
    cear.lp = ifelse(frame.nm == 'Loco' 
                           & performance.nm == 'Low performance', 1, 0),
    oa.lp = ifelse(frame.nm == 'Hake' 
                           & performance.nm == 'Low performance', 1, 0),
    peer.enf.hp = ifelse(stage.nm == 'Peer-enforced' &
                                  performance.nm == 'High performance', 1, 0), 
    cear.hp.non.enf.rounds = ifelse(frame.nm == 'Loco'&
                                    performance.nm == 'High performance'& 
                                    round < 11, 
                                    round - 1, 0), 
    cear.hp.peer.enf.rounds = ifelse(frame.nm == 'Loco' &
                                    performance.nm == 'High performance'& 
                                    round > 10,
                                    round - 11, 0), 
    oa.hp.non.enf.rounds = ifelse(frame.nm == 'Hake'&
                                    performance.nm == 'High performance'& 
                                    round < 11, 
                                    round - 1, 0),
    oa.hp.peer.enf.rounds = ifelse(frame.nm == 'Hake'&
                                    performance.nm == 'High performance'& 
                                    round > 10, 
                                    round - 11, 0),
    cear.lp.non.enf.rounds = ifelse(frame.nm == 'Loco'&
                                    performance.nm == 'Low performance'& 
                                    round < 11, 
                                    round - 1, 0), 
    cear.lp.peer.enf.rounds = ifelse(frame.nm == 'Loco'&
                                    performance.nm == 'Low performance'& 
                                    round > 10, 
                                    round - 11, 0), 
    oa.lp.non.enf.rounds = ifelse(frame.nm == 'Hake'&
                                    performance.nm == 'Low performance'& 
                                    round < 11, 
                                    round - 1, 0),
    oa.lp.peer.enf.rounds = ifelse(frame.nm == 'Hake'&
                                    performance.nm == 'Low performance'& 
                                    round > 10, 
                                    round - 11, 0), 
    # creating weights to run weighted regressions means for groups 999 and 888 come from 10 subjects while means for other groups come from only 5 subjects
    weights = ifelse(group.id.fixed == '999' | group.id.fixed == '888', 1, 0.5))
```

```{r running linear models for group compliance, echo = FALSE, results = 'asis', warnings = FALSE, messages = FALSE}

# running the weighted OLS of group compliance in each round

comp.grp.1 <- lm(mean.group.com ~ cear, data = db.group, weights = weights)
comp.grp.2 <- lm(mean.group.com ~ cear + peer.enf + hp, data = db.group, weights = weights)
comp.grp.3 <- lm(mean.group.com ~ cear + peer.enf + hp + non.enf.rounds + peer.enf.rounds, data = db.group, weights = weights)
comp.grp.4 <- lm(mean.group.com ~ cear + peer.enf + hp + cear.peer.enf + cear.hp + peer.enf.hp, data = db.group, weights = weights)
comp.grp.5 <- lm(mean.group.com ~ cear + peer.enf + hp + non.enf.rounds + peer.enf.rounds + cear.peer.enf + cear.hp + peer.enf.hp, data = db.group, weights = weights)
comp.grp.6 <- lm(mean.group.com ~ cear + peer.enf + hp + cear.peer.enf + cear.hp + peer.enf.hp +  cear.hp.non.enf.rounds + cear.hp.peer.enf.rounds + oa.hp.non.enf.rounds + oa.hp.peer.enf.rounds + cear.lp.non.enf.rounds + cear.lp.peer.enf.rounds + oa.lp.non.enf.rounds + oa.lp.peer.enf.rounds, data = db.group, weights = weights)

# adjusting standard errors to robust

comp.grp.1.cov <- vcovHC(comp.grp.1, type = "HC1")
comp.grp.1.se <- sqrt(diag(comp.grp.1.cov))

comp.grp.2.cov <- vcovHC(comp.grp.2, type = "HC1")
comp.grp.2.se <- sqrt(diag(comp.grp.2.cov))

comp.grp.3.cov <- vcovHC(comp.grp.3, type = "HC1")
comp.grp.3.se <- sqrt(diag(comp.grp.3.cov))

comp.grp.4.cov <- vcovHC(comp.grp.4, type = "HC1")
comp.grp.4.se <- sqrt(diag(comp.grp.4.cov))

comp.grp.5.cov <- vcovHC(comp.grp.5, type = "HC1")
comp.grp.5.se <- sqrt(diag(comp.grp.5.cov))

comp.grp.6.cov <- vcovHC(comp.grp.6, type = "HC1")
comp.grp.6.se <- sqrt(diag(comp.grp.6.cov))

# computing AIC scores

comp.grp.1.aic <- round(AIC(comp.grp.1), 2)
comp.grp.2.aic <- round(AIC(comp.grp.2), 2)
comp.grp.3.aic <- round(AIC(comp.grp.3), 2)
comp.grp.4.aic <- round(AIC(comp.grp.4), 2)
comp.grp.5.aic <- round(AIC(comp.grp.5), 2)
comp.grp.6.aic <- round(AIC(comp.grp.6), 2)

# Printing results 

stargazer(comp.grp.1, comp.grp.2, comp.grp.3, comp.grp.4, comp.grp.5, comp.grp.6, type = 'html', digits = 2, se = list(comp.grp.1.se, comp.grp.2.se, comp.grp.3.se, comp.grp.4.se, comp.grp.5.se, comp.grp.6.se), notes = "Robust standard errors", covariate.labels = c("CEAR", "Peer-enforced stage", "HP", "Non-enforced rounds", "Peer-enforced rounds", "CEAR x Peer-enf. stage", "CEAR x HP", "Peer-enf. stage x HP", "CEAR × HP × Non-enf. rounds", "CEAR × HP × Peer-enf. rounds", "Pseudo-OA × HP × Non-enf. rounds", "Pseudo-OA × HP × Peer-enf. rounds", "CEAR × LP × Non-enf. rounds", "CEAR × LP × Peer-enf. rounds", "Pseudo-OA × LP × Non-enf. rounds", "Pseudo-OA × LP × Peer-enf. rounds", "Constant"), dep.var.labels = "Group percent of compliance", omit.stat = "f", add.lines = list(c("AIC", comp.grp.1.aic, comp.grp.2.aic, comp.grp.3.aic, comp.grp.4.aic, comp.grp.5.aic, comp.grp.6.aic)), df = F, title = "Weighted linear regressions of group percent of compliance in each round on treatment, association type, stage, rounds and their interaction. The weight for each observation is assigned based on the number of subjects playing in each group (all groups have five players except for two groups of ten players). Different columns present different model specifications.", ci = T)

```

## **3. Differences in peer-enforcement** {.tabset}

### 3.a. Nonparametric test for differences in individual report probability (Appendix S9)
```{r non-parametric comparisons of individual report probability, echo = FALSE, message=FALSE, warning=FALSE}

# computing probability of report aggregated over rounds at the individual level

db.report.ind <- db %>% 
  filter(round > 10) %>% 
  # subjects only had the opportunity to report if they were assigned observers and the inspected subject overharvested
  mutate(report.opportunity = ifelse(observer ==1 & overext_observed > 0, 1, 0)) %>% 
  group_by(frame.nm, performance.nm, id) %>% 
  summarise(prob.report = sum(report, na.rm=T)/sum(report.opportunity, na.rm=T)) %>% 
  select(-id) %>% 
  filter(!(prob.report == 'NaN'))

n.report <- db.report.ind %>% 
  group_by(frame.nm, performance.nm) %>% 
  summarise(n = length(prob.report))

# Testing significant differences in individual report probability between frame and performance 

test.report.frame <- db.report.ind %>%
  group_by(performance.nm) %>% 
  summarize(p.value = wilcox.test(prob.report ~ as.factor(frame.nm))$p.value, 
            statistic = wilcox.test(prob.report ~ as.factor(frame.nm))$statistic) %>% 
  mutate(frame.nm = 'vs')

test.report.performance <- db.report.ind %>%
  group_by(frame.nm) %>% 
  summarize(p.value = wilcox.test(prob.report ~ as.factor(performance.nm))$p.value, 
            statistic = wilcox.test(prob.report ~ as.factor(performance.nm))$statistic) %>% 
  mutate(performance.nm = 'vs') 


test.report<- rbind(test.report.frame, test.report.performance) %>% 
  mutate(corrected.p.value = p.value * 4, 
         sign.corrected = ifelse(corrected.p.value < 0.05,"*", "")) %>% 
  select(performance.nm, frame.nm, statistic, p.value, corrected.p.value)

wilx.report <- gt(test.report) %>% 
   fmt_number(columns = vars(p.value, corrected.p.value), decimals = 3) %>% 
  tab_header(
    title = md("Wilcoxon rank-sum test: differences in individual probability of reporting")
  ) %>% 
  tab_source_note(
    source_note = md("Significance level is ajusted using a Bonferroni correction for 4 hypotheses")
  )

wilx.report
```

### 3.b. Plot of mean individual probability of reporting per treatment and association type (Fig. 2)
```{r bar plot probability of reporting, echo = FALSE, message=FALSE, warning=FALSE, fig.cap= '**Fig 2.** Mean probability of reporting a peer to authorities in the common-pool-resource game due to noncompliance with the individual quota of loco, which is fished under collective, exclusive access (CEAR) in real life, and due to noncompliance with the individual quota of hake, which is fished under pseudo-open access (OA) in real life for high-performance associations and low-performance associations (error bars, 95% CIs computed at the individual level). Sample sizes differ because the inspector role was randomly assigned in each round and inspectors could only report if the inspected fisher had overharvested. Therefore, not every fisher had an opportunity to report (for high-performance associations under collective, exclusive access treatment, n = 22; for high-performance associations pseudo-open access treatment, n = 30; for low-performance associations under collective, exclusive access treatment, n = 30; for low-performance associations under pseudo-open access treatment, n = 28).'}

# summary statistic for bar plot on individual probability of reporting
db.report.plot<- db.report.ind %>% 
  group_by(frame.nm, performance.nm) %>% 
  summarise(mean = mean(prob.report),
          sd = sd(prob.report),
          n = length(prob.report)) %>% 
  mutate(error = qnorm(0.975)*(sd/sqrt(n)), 
         ci.low = mean - error, 
         ci.high = mean + error) %>% 
  rename(
    Performance = performance.nm,
    Frame = frame.nm
  )

# plotting 
plot.report <- ggplot(db.report.plot, aes(x= Performance, y= mean, fill= reorder(Frame, -mean))) + 
    geom_bar(stat='identity', width=0.5, position=position_dodge(0.6))+
  geom_errorbar(aes(x=as.factor(Performance), ymin = ci.low, ymax= ci.high), width=0.25, position=position_dodge(0.6), size = 0.4)+
  scale_fill_manual(values = c("royalblue3", "red1"), labels = c("CEAR (Loco)", "pseudo-OA (Hake)"))+
  xlab(expression(bold("Association type")))+
  ylab(expression(bold("Probability of reporting")))+
  scale_y_continuous(expand = c(0, 0), limits=c(0,1), breaks=seq(0,1, by=0.2))+
  #facet_wrap(~Performance)+
  #scale_x_discrete(labels=c("1" = "High-performance", "2" = "Low-performance"))+ 
  theme_bw()+
  theme(legend.position="top", legend.title=element_blank(), legend.text = element_text(size=10, margin = margin(t= 10, r= 0, b =0, l =0)), 
        panel.grid = element_blank(), 
        strip.text = element_text(size=11), 
        axis.title = element_text(size = 12), 
        axis.text = element_text(size = 11), 
        axis.title.y = element_text(margin = margin(t = 0, r = 8, b = 0, l = 0)), 
        axis.title.x = element_text(margin = margin(t = 8, r = 0, b = 0, l = 0)))

plot.report
#ggsave("Fig2_rev_rev.pdf", plot = plot.report, device = "pdf", path = here::here("figures"), scale = 1, width = 16, height = 12, units = "cm", dpi = 600, limitsize = TRUE)


```

### 3.c. Weighted OLS of group probability of reporting on treatment, association type and stage variables (Appendix S10)
```{r running linear models for group probability of reporting, echo = FALSE, results = 'asis', warnings = FALSE, messages = FALSE}

# running the weighted OLS of group probability of reportingin each round 

report.grp.1 <- lm(group.prob.report ~ cear, data = subset(db.group, db.group$round > 10), weights = weights)

report.grp.2 <- lm(group.prob.report ~ cear + round + mean.obs.overharvest, data = subset(db.group, db.group$round > 10), weights = weights)

report.grp.3 <- lm(group.prob.report ~ cear + hp, data = subset(db.group, db.group$round > 10), weights = weights)

report.grp.4 <- lm(group.prob.report ~ cear + round + mean.obs.overharvest + hp, data = subset(db.group, db.group$round > 10), weights = weights)

report.grp.5 <- lm(group.prob.report ~ cear + hp + cear.hp, data = subset(db.group, db.group$round > 10), weights = weights)

report.grp.6 <- lm(group.prob.report ~ cear + round + mean.obs.overharvest + hp + cear.hp, data = subset(db.group, db.group$round > 10), weights = weights)

report.grp.7 <- lm(group.prob.report ~ cear.hp + oa.hp + cear.lp + oa.lp -1, data = subset(db.group, db.group$round > 10), weights = weights)

report.grp.8 <- lm(group.prob.report ~ round + mean.obs.overharvest + cear.hp + oa.hp + cear.lp + oa.lp -1, data = subset(db.group, db.group$round > 10), weights = weights)

# adjusting standard errors to robust

report.grp.1.cov <- vcovHC(report.grp.1, type = "HC1")
report.grp.1.se <- sqrt(diag(report.grp.1.cov))

report.grp.2.cov <- vcovHC(report.grp.2, type = "HC1")
report.grp.2.se <- sqrt(diag(report.grp.2.cov))

report.grp.3.cov <- vcovHC(report.grp.3, type = "HC1")
report.grp.3.se <- sqrt(diag(report.grp.3.cov))

report.grp.4.cov <- vcovHC(report.grp.4, type = "HC1")
report.grp.4.se <- sqrt(diag(report.grp.4.cov))

report.grp.5.cov <- vcovHC(report.grp.5, type = "HC1")
report.grp.5.se <- sqrt(diag(report.grp.5.cov))

report.grp.6.cov <- vcovHC(report.grp.6, type = "HC1")
report.grp.6.se <- sqrt(diag(report.grp.6.cov))

report.grp.7.cov <- vcovHC(report.grp.7, type = "HC1")
report.grp.7.se <- sqrt(diag(report.grp.7.cov))

report.grp.8.cov <- vcovHC(report.grp.8, type = "HC1")
report.grp.8.se <- sqrt(diag(report.grp.8.cov))

# computing AIC scores

report.grp.1.aic <- round(AIC(report.grp.1), 2)
report.grp.2.aic <- round(AIC(report.grp.2), 2)
report.grp.3.aic <- round(AIC(report.grp.3), 2)
report.grp.4.aic <- round(AIC(report.grp.4), 2)
report.grp.5.aic <- round(AIC(report.grp.5), 2)
report.grp.6.aic <- round(AIC(report.grp.6), 2)
report.grp.7.aic <- round(AIC(report.grp.7), 2)
report.grp.8.aic <- round(AIC(report.grp.8), 2)

# printing results 

stargazer(report.grp.1, report.grp.2, report.grp.3, report.grp.4, report.grp.5, report.grp.6, report.grp.7, report.grp.8, type = 'html', digits = 2, se = list(report.grp.1.se, report.grp.2.se, report.grp.3.se, report.grp.4.se, report.grp.5.se, report.grp.6.se, report.grp.7.se, report.grp.8.se), covariate.labels = c("CEAR", "Round", "Mean observed overharvest", "HP", "CEAR × HP", "Pseudo-OA x HP", "CEAR × LP", "Pseudo-OA × LP", "Constant"), dep.var.labels = "Group probability of reporting", omit.stat = "f", add.lines = list(c("AIC", report.grp.1.aic, report.grp.2.aic, report.grp.3.aic, report.grp.4.aic, report.grp.5.aic, report.grp.6.aic, report.grp.7.aic, report.grp.8.aic)), df = F, notes = "Robust standard errors", title = "Weighted linear regression of group probability of reporting in each round over treatment, association type, stage, rounds and their interaction. The weight for each observation is assigned based on the number of subjects playing in each group (all groups have five players except for two groups of ten players). Different columns present different model specifications.", ci = T)
```

## **4. The effect of peer-enforcement on compliance** {.tabset}

### 4.a. Nonparametric tests for evolution of compliance (Appendix S11)
```{r non-parametric comparisons of first and last rounds per treatment, echo = FALSE, message=FALSE, warning=FALSE}

# Filtering only first and last round of non-enforced stage

db.evol.nonenf <- db %>% 
  filter(round == 1|round == 10)

# Testing significant differences between first and last round for each frame performance combination in non-enforced stage

evol.nonenf <- db.evol.nonenf %>%
  group_by(performance.nm, frame.nm) %>% 
  summarize(p.value = wilcox.test(compliance ~ as.factor(round), paired = T)$p.value,
            statistic = wilcox.test(compliance ~ as.factor(round), paired = T)$statistic) %>% 
  mutate(stage = "nonenforced")

# filtering only first and last round of peer-enforced stage

db.evol.peerenf <- db %>% 
  filter(round == 11|round == 20)

# testing significant differences between first and last round for each frame performance combination in peer-enforced stage

evol.peerenf <- db.evol.peerenf %>%
  group_by(performance.nm, frame.nm) %>% 
  summarize(p.value = wilcox.test(compliance ~ as.factor(round), paired = T)$p.value,
            statistic = wilcox.test(compliance ~ as.factor(round), paired = T)$statistic)%>% 
  mutate(stage = "peer-enforced")

# unifying outputs

test.evol <- rbind(evol.nonenf, evol.peerenf) %>% 
  select(performance= performance.nm, frame = frame.nm, stage, statistic, p.value) %>% 
  mutate(corrected.p.value = p.value*8, 
         sign.corrected = ifelse(corrected.p.value < 0.05,"**", "")) # Correcting for 8 hypotheses using Bonferroni

wilx.evol.com <- gt(test.evol) %>% 
   fmt_number(columns = vars(p.value, corrected.p.value), decimals = 3) %>% 
 tab_header(
    title = md("Wilcoxon rank-sum paired test: differences in compliance between the first and last round in each stage")
  ) %>% 
  tab_source_note(
    source_note = md("Significance level is ajusted using a Bonferroni correction for 8 hypotheses")
  )

wilx.evol.com

```

### 4.b. Plot of evolution of individual compliance (Fig. 3)
```{r plot evolution of individual compliance by stage, echo = FALSE, message= FALSE, warning=FALSE, fig.cap='**Fig. 3.** Mean percent compliance in the common-pool-resource game with the individual quota of loco, which is fished under collective, exclusive access (CEAR) in real life, and with the individual quota of hake, which is fished under pseudo-OA (OA) in real life for high-performance associations and low-performance associations in early (rounds 1,2, and 3), middle (rounds 4,5,6, and 7), and late (rounds 8, 9, and 10) rounds of the unenforced and peer-enforced stages of the game  (error bars, 95% CIs computed at the individual level; n = 30).'}

# computing summary statistics for plot on individual compliance per stage

db.evol.plot <- db %>% 
  mutate(stage.three = case_when(round == 1 ~ 'Early',
                                 round == 2 ~ 'Early', 
                                 round == 3 ~ 'Early',
                                 round == 4 ~ 'Mid',
                                 round == 5 ~ 'Mid',
                                 round == 6 ~ 'Mid',
                                 round == 7 ~ 'Mid',
                                 round == 8 ~ 'Late',
                                 round == 9 ~ 'Late',
                                 round == 10 ~ 'Late',
                                 round == 11 ~ 'Early',
                                 round == 12 ~ 'Early', 
                                 round == 13 ~ 'Early',
                                 round == 14 ~ 'Mid',
                                 round == 15 ~ 'Mid',
                                 round == 16 ~ 'Mid',
                                 round == 17 ~ 'Mid',
                                 round == 18 ~ 'Late',
                                 round == 19 ~ 'Late',
                                 round == 20 ~ 'Late'),
         stage.nm = fct_relevel(stage.nm, c("Unenforced", "Peer enforced"))) %>% 
  group_by(performance.nm, frame.nm, stage.nm, stage.three) %>% 
  summarize(mean.compliance = mean(compliance),
            sd = sd(compliance),
            n = length(compliance)) %>% 
  ungroup() %>% 
  mutate(error = qnorm(0.975)*(sd/sqrt(n)), 
         ci.low = mean.compliance - error, 
         ci.high = mean.compliance + error,
         stage.three = factor(stage.three, levels = c("Early", "Mid", "Late")))

plot.high <- ggplot(subset(db.evol.plot, performance.nm == "High performance"), aes(x= stage.three, y= mean.compliance, group=frame.nm)) +
  geom_line(aes(col= frame.nm), size = 0.64) +
  geom_point(aes(col = frame.nm), size = 1.3) +
  geom_errorbar(aes(ymin=ci.low, ymax= ci.high, col = frame.nm), width= 0.28) +
  scale_color_manual(values = c("red1", "royalblue3"), labels = c("pseudo-OA (Hake)", "CEAR (Loco)"))+
  scale_fill_manual(values = c("red1", "royalblue3"), labels = c("pseudo-OA (Hake)", "CEAR (Loco)"))+
  theme_bw() + 
  ggtitle('High-performance associations')+
  xlab(expression(bold("Rounds"))) +
  ylab(expression(bold("Compliance (%)")))+
  #scale_x_continuous(expand = c(0,0), breaks=c(seq(1,20,1)), labels = c(seq(0,9,1), seq(0,9,1)))+
  scale_y_continuous(limits = c(0,100), breaks = c(seq(0,100,20)), expand = c(0,0))+
  #geom_vline(xintercept=10.5, size=5.4, col= 'white')+
  facet_wrap(~stage.nm)+
  theme(legend.position="top", legend.title=element_blank(), legend.text =    element_text(size=11), panel.grid = element_blank(), plot.title = element_text(hjust = 0.5), panel.grid.major = element_blank(), panel.grid.minor = element_blank())+
  theme(panel.grid.major = element_blank(),
        panel.grid.minor = element_blank(),
        #strip.background = element_blank(),
        strip.text = element_text(size= 10, hjust = 0, vjust = 1),
        panel.border = element_rect(colour = "dark grey"), 
        panel.spacing.x=unit(1, "lines"), 
        axis.title.x = element_text(margin = margin(t = 10, r = 0, b = 0, l = 0)), 
        #axis.title = element_text(size = 11), 
        axis.title = element_blank(),
        axis.text = element_text(size = 10),
        plot.title = element_text(size= 11, face= "bold", hjust = 0, vjust = 1))

# Extracxt the legend from p1
legend = gtable_filter(ggplotGrob(plot.high), "guide-box") 



plot.low <- ggplot(subset(db.evol.plot, performance.nm == "Low performance"), aes(x= stage.three, y= mean.compliance, group=frame.nm)) +
  geom_line(aes(col= frame.nm), size = 0.64) +
  geom_point(aes(col = frame.nm), size = 1.3) +
  geom_errorbar(aes(ymin=ci.low, ymax= ci.high, col = frame.nm), width= 0.28) +
  scale_color_manual(values = c("red1", "royalblue3"), labels = c("pseudo-OA (Hake)", "CEAR (Loco)"))+
  scale_fill_manual(values = c("red1", "royalblue3"), labels = c("pseudo-OA (Hake)", "CEAR (Loco)"))+
  theme_bw() + 
  ggtitle('Low-performance associations')+
  xlab(expression(bold("Rounds"))) +
  ylab(expression(bold("Compliance (%)")))+
  #scale_x_continuous(expand = c(0,0), breaks=c(seq(1,20,1)), labels = c(seq(0,9,1), seq(0,9,1)))+
  scale_y_continuous(limits = c(0,100), breaks = c(seq(0,100,20)), expand = c(0,0))+
  #geom_vline(xintercept=10.5, size=5.4, col= 'white')+
  facet_wrap(~stage.nm)+
  theme(legend.position="top", legend.title=element_blank(), legend.text =    element_text(size=11),
        panel.grid = element_blank(), plot.title = element_text(hjust = 0.5), panel.grid.major =
          element_blank(), panel.grid.minor = element_blank())+
  theme(panel.grid.major = element_blank(),
        panel.grid.minor = element_blank(),
        #strip.background = element_blank(),
        strip.text = element_text(size= 10, hjust = 0, vjust = 1),
        panel.border = element_rect(colour = "dark grey"), 
        panel.spacing.x=unit(1, "lines"), 
        axis.title.x = element_text(margin = margin(t = 10, r = 0, b = 0, l = 0)), 
        axis.title = element_blank(), 
        axis.text = element_text(size = 10),
        plot.title = element_text(size= 11, face= "bold", hjust = 0, vjust = 1))

evol.compliance <- gridExtra::grid.arrange(legend, gridExtra::arrangeGrob(plot.high + theme(legend.position="none"), 
                         plot.low + theme(legend.position="none"),
                         ncol = 2,
                         left = textGrob("Compliance (%)", rot = 90, vjust = 0.9, gp = gpar(fontface = "bold", cex = 0.98))), 
                         nrow = 2, 
                         heights = c(0.2,1.8))


evol.compliance
#ggsave("Fig3_rev_rev.pdf", plot = evol.compliance, device = "pdf", path = here::here("figures"), scale = 1, width = 18, height = 12, units = "cm", dpi = 600, limitsize = TRUE)


```

## **5. Exploring correlates of individual compliance and enforcement decisions (Appendix S6) ** {.tabset}

```{r creating db at the individual level, echo = FALSE, message= FALSE, warning = FALSE}

db.ind <- db %>% 
   # creating dummies and interactions for frame, associations and stage 
   mutate(
    # transforming NAs to zeroes for cumulative variables
    punished.na.to.zero = ifelse(is.na(punished), 0, punished), 
    report.na.to.zero = ifelse(is.na(report), 0, report),
    # variables for rounds in each stage
    non.enf.rounds = ifelse(round <= 10, round - 1, 0),
    peer.enf.rounds = ifelse(round > 10, round - 11, 0), 
    # punishment
    enf.stage = ifelse(stage ==1, 0, 1),
    # variable to mark first round 
    first.round = ifelse(round == 1, 1, 0), 
    # variable to mark last round 
    last.round = ifelse(round == 20, 1, 0), 
    # variable to mark peer-enf rounds
    peer.enf.stage = ifelse(round > 10, 1, 0)) %>% 
  # creating variables in Cassari and Luni, 2009
  ## avg compliance in non-enf stage per individual
  group_by(id) %>%
  mutate(avg.comp.non.enf = mean(compliance[round<11])) %>% 
  ungroup() %>% 
  ## avg compliance and overharvest in the group in round t
  ### grouping by group_id in each round
  group_by(group_id, round) %>% 
  mutate(sum.comp = sum(compliance),
         sum.overextr = sum(overextraction),
         avg.group.comp = sum.comp/5,
         avg.group.overextr = sum.overextr/5) %>% 
  ungroup() %>% 
  ## avg compliance and overextraction of other group members in round t
  mutate(avg.oth.comp = (sum.comp - compliance)/4,
         avg.oth.overextr = (sum.overextr - overextraction)/4,
         sum.overextr.oth = sum.overextr - overextraction) %>% 
  group_by(id) %>% 
  ## avg compliance and overextraction of other group members in previous round 
  mutate(avg.oth.comp.prev = dplyr::lag(avg.oth.comp, n=1),
         avg.oth.overextr.prev = dplyr::lag(avg.oth.overextr, n=1),
         ## average group compliance in the previous round
         avg.group.comp.prev = dplyr::lag(avg.group.comp, n=1),
         avg.group.overextr.prev = dplyr::lag(avg.group.overextr, n=1),
         ## average others' compliance interacted with non-enforced stage
         avg.oth.comp.prev.non.enf = ifelse(round < 11, avg.group.comp.prev, 0),
         ## average others' compliance interacted with enforced stage
         avg.oth.comp.prev.peer.enf = ifelse(round > 10, avg.group.comp.prev, 0),
         ## transforming non-punished in zeroes for peer-enforced stage and into NAs in non-enforced stage
         punished.fixed = ifelse(round > 10 & is.na(punished), 0, punished),
         ## subject was reported in previous round
         punished.prev.round = dplyr::lag(punished.fixed),
         ## subject was punished in the second previous round
         punished.prev.prev.round = dplyr::lag(punished.prev.round),
         ## transforming non-report in zeroes for peer-enforced stage and into NAs in non-enforced stage
         report.fixed = ifelse(round > 10 & is.na(report), 0, report),
         ## subject reported in previous round
         report.prev.round = dplyr::lag(report.fixed),
         ## subject reported in the second previous round
         report.prev.prev.round = dplyr::lag(report.prev.round),
         ## recent punishment
         recently.punished = ifelse(round > 10, ifelse(punished.prev.round ==1 | punished.prev.prev.round == 1, 1, 0), NA),
         ## recent report
         recently.report = ifelse(round > 10, ifelse(report.prev.round ==1 | report.prev.prev.round == 1, 1, 0), NA),
         ## cumulative punishment at round t
         cumul.punished = cumsum(punished.na.to.zero), 
         cumul.punished = ifelse(round > 10, lag(cumul.punished), NA),
         ## cumulative reports
         cumul.report= cumsum(report.na.to.zero),
         cumul.report = ifelse(round > 10, lag(cumul.report), NA)
         
         ) %>% 
  ungroup() %>% 
  mutate(
    ## whether the subject had been punished at least once by that round
    punished.binary = ifelse(cumul.punished > 0, 1, 0),
    punished.binary = ifelse(round > 10, punished.binary, NA),
    report.binary = ifelse(cumul.punished > 0, 1, 0),
    report.binary = ifelse(round > 10, report.binary, NA),
    ## compliance deviation from exogenous rule 
    obs.comp = ((50 - overext_observed) * 100)/50,
    ## deviation of inspected compliance relative to average group compliance in prev round
    dev.group = obs.comp - avg.group.comp.prev,
    ## deviation of inspected relative to inspector's compliance in that round
    dev.inspector = obs.comp - compliance,
    ## positive deviation of inspected relative to average group compliance in prev round
    pos.dev.group = ifelse(dev.group > 0 , dev.group, 0),
    ## negative deviation of inspected relative to average group compliance in prev round
    neg.dev.group = ifelse(dev.group < 0 , abs(dev.group), 0),
    ## positive deviation of inspected relative to inspector's compliance 
    pos.dev.inspector = ifelse(dev.inspector > 0 , dev.inspector, 0),
    ## negative deviation of inspected relative to inspector compliance in that round
    neg.dev.inspector = ifelse(dev.inspector < 0 , abs(dev.inspector), 0))

```

All NAs observations related to reports were replaced with zeroes.

```{r changing NAs for zeroes for rounds with no punishment, echo= FALSE, message= FALSE, warning=FALSE}

db.ind.no.nas <- db.ind %>% 
  mutate(punished.prev.round = ifelse(is.na(punished.prev.round), 0, punished.prev.round),
         punished.prev.prev.round = ifelse(is.na(punished.prev.prev.round), 0, punished.prev.prev.round),
         report.prev.round = ifelse(is.na(report.prev.round), 0, report.prev.round),
         report.prev.prev.round = ifelse(is.na(report.prev.prev.round), 0, report.prev.prev.round),
         cumul.punished = ifelse(is.na(cumul.punished), 0, cumul.punished),
         cumul.report = ifelse(is.na(cumul.report), 0, cumul.report),
         punished.binary = ifelse(is.na(punished.binary), 0, punished.binary),
         report.binary = ifelse(is.na(report.binary), 0, report.binary),
         recently.punished = ifelse(is.na(recently.punished), 0, recently.punished),
         recently.report = ifelse(is.na(recently.report), 0, recently.report))
```

### 5.a Individual determinants of compliance (Linear mixed models with individual random effects - Appendix S6, Table S2)
```{r lmm for determinants of individual compliance with individual random effects and punishment previous round, echo = FALSE, results = 'asis', warnings = FALSE, messages = FALSE}

comp.ind.hp.cear.1 <- lme(compliance ~ avg.oth.comp.prev.non.enf + avg.oth.comp.prev.peer.enf + punished.prev.round + enf.stage, random=~1|id, na.action= na.exclude, data = filter(db.ind.no.nas, performance.nm == 'High performance' & frame.nm =="Loco" & round != 11))

comp.ind.hp.oa.1 <- lme(compliance ~ avg.oth.comp.prev.non.enf + avg.oth.comp.prev.peer.enf + punished.prev.round + enf.stage, random=~1|id, na.action= na.exclude, data = filter(db.ind.no.nas, performance.nm == 'High performance' & frame.nm =="Hake" & round != 11))

comp.ind.lp.cear.1 <- lme(compliance ~ avg.oth.comp.prev.non.enf + avg.oth.comp.prev.peer.enf + punished.prev.round + enf.stage, random=~1|id, na.action= na.exclude, data = filter(db.ind.no.nas, performance.nm == 'Low performance' & frame.nm =="Loco" & round != 11))

comp.ind.lp.oa.1 <- lme(compliance ~ avg.oth.comp.prev.non.enf + avg.oth.comp.prev.peer.enf + punished.prev.round + enf.stage, random=~1|id, na.action= na.exclude, data = filter(db.ind.no.nas, performance.nm == 'Low performance' & frame.nm =="Hake" & round != 11))


# Printing results 

stargazer(comp.ind.hp.cear.1, comp.ind.hp.oa.1, comp.ind.lp.cear.1, comp.ind.lp.oa.1, type = 'html', digits = 2, column.labels = c("HP-CEAR", "HP-OA", "LP-CEAR", "LP-OA"), dep.var.labels = "Individual percent of compliance", covariate.labels = c("Average compliance of other group members in previous round in the non-enfoced stage", "Average compliance of other group members in previous round in the peer-enfoced stage","Subject was reported in the previous round","Peer-enforced stage", "Constant"), title = "Linear regressions of individual percent of compliance in each round over variables given by subjects' behavior in the game. Regressions include individual random effects. Each column presents the results for one treatment-association type combination.", ci = T)

```

### 5.b Individual determinants of peer enforcement (Probit model with individual random effects- Appendix S6, Table S3) 

```{r probit models for determinants of individual reports exo.rule 3, echo = FALSE, results = 'asis', warnings = FALSE, messages = FALSE}

report.ind.hp.cear.3 <- glmer(report ~ obs.comp + punished.prev.round + avg.comp.non.enf + (1|id), na.action= na.exclude, data = filter(db.ind, performance.nm == 'High performance' & frame.nm =="Loco" & observer == 1 & overext_observed > 0), family = binomial(link = "probit"))

report.ind.hp.oa.3 <- glmer(report ~  obs.comp +  punished.prev.round + avg.comp.non.enf + (1|id), na.action= na.exclude, data = filter(db.ind, performance.nm == 'High performance' & frame.nm =="Hake" & observer == 1 & overext_observed > 0), family = binomial(link = "probit"))

report.ind.lp.cear.3 <- glmer(report ~  obs.comp +  punished.prev.round + avg.comp.non.enf + (1|id), na.action= na.exclude, data = filter(db.ind, performance.nm == 'Low performance' & frame.nm =="Loco" & observer == 1 & overext_observed > 0), family = binomial(link = "probit"))

report.ind.lp.oa.3 <- glmer(report ~ obs.comp +  punished.prev.round + avg.comp.non.enf + (1|id), na.action= na.exclude, data = filter(db.ind, performance.nm == 'Low performance' & frame.nm =="Hake" & observer == 1 & overext_observed > 0), family = binomial(link = "probit"))

# Printing results 

stargazer(report.ind.hp.cear.3, report.ind.hp.oa.3, report.ind.lp.cear.3, report.ind.lp.oa.3, type = 'html', digits = 2, column.labels = c("HP-CEAR", "HP-OA", "LP-CEAR", "LP-OA"), dep.var.labels = "Report (Yes =1, No = 0)", covariate.labels = c("Percent of compliance of inspected fisher", "Subject was rpeorted in the previous round", "Average compliance of the subject in the non-enforced stage", "Constant"), title = "Probit models of individual reporting decisions in each round over variables given by subjects' behavior in the game. Each column presents the results for one treatment-association type combination. Models include individual random effects", ci = T)

```


## **6. Cost benefit of enforcement (Appendix S12 and S13)**

```{r  Cost benefit, echo = FALSE, warning = FALSE, message= FALSE}

# table considering costs for the regulator

cb.enf.cost.reg <-  db.ind %>% 
  select(id, 
         performance, 
         framing,
         group_id, 
         round, 
         overextraction, 
         observer, 
         overext_observed, 
         report, punished, 
         round_profit, 
         group.id.fixed, 
         stage, 
         punished.na.to.zero, 
         report.na.to.zero, 
         sum.overextr, 
         sum.overextr.oth) %>% 
  mutate(
    # renamimng variables
    frame = ifelse(framing == 1, "Loco", "Hake"),
    performance = ifelse(performance == 1, "High-performance", "Low-performance"),
    # not considering gains for being assigned an inspector
    profit.round = (100 + overextraction - (0.5 * sum.overextr.oth))* 10,
    profit.round = ifelse(punished.na.to.zero == 1, 0, profit.round),
    # subjects that were payed 250 in each round
    payed.inspector = ifelse(observer == 1 & overext_observed > 0, 1, 0),
    stage = ifelse(round > 10, "Peer-enforced", "Non-enforced")
  ) %>% 
  group_by(performance, 
           frame, 
           stage) %>% 
  summarise(
    n.payed.inspectors = sum(payed.inspector),
    total.profit = sum(profit.round),
    total.cost  = ifelse(is.na(n.payed.inspectors), 0, n.payed.inspectors*250),
    net.earnings = (total.profit - total.cost)
    #net.earnings = total.profit
  ) %>% 
  select(-c(n.payed.inspectors, total.profit, total.cost)) %>% 
  spread(stage, net.earnings) %>% 
  rename(net.earnings.enf = "Peer-enforced", 
         net.earnings.non.enf = "Non-enforced") %>% 
  mutate(net.gains = net.earnings.enf - net.earnings.non.enf)

# table considering only payoffs for the fisher

cb.enf.no.cost.reg <-  db.ind %>% 
  select(id, 
         performance, 
         framing,
         group_id, 
         round, 
         overextraction, 
         observer, 
         overext_observed, 
         report, punished, 
         round_profit, 
         group.id.fixed, 
         stage, 
         punished.na.to.zero, 
         report.na.to.zero, 
         sum.overextr, 
         sum.overextr.oth) %>% 
  mutate(
    # renamimng variables
    frame = ifelse(framing == 1, "Loco", "Hake"),
    performance = ifelse(performance == 1, "High-performance", "Low-performance"),
    # not considering gains for being assigned an inspector
    profit.round = (100 + overextraction - (0.5 * sum.overextr.oth))* 10,
    profit.round = ifelse(punished.na.to.zero == 1, 0, profit.round),
    # subjects that were payed 250 in each round
    payed.inspector = ifelse(observer == 1 & overext_observed > 0, 1, 0),
    stage = ifelse(round > 10, "Peer-enforced", "Non-enforced")
  ) %>% 
  group_by(performance, 
           frame, 
           stage) %>% 
  summarise(
    n.payed.inspectors = sum(payed.inspector),
    total.profit = sum(profit.round),
    total.cost  = ifelse(is.na(n.payed.inspectors), 0, n.payed.inspectors*250),
    #net.earnings = (total.profit - total.cost)
    net.earnings = total.profit
  ) %>% 
  select(-c(n.payed.inspectors, total.profit, total.cost)) %>% 
  spread(stage, net.earnings) %>% 
  rename(net.earnings.enf = "Peer-enforced", 
         net.earnings.non.enf = "Non-enforced") %>% 
  mutate(net.gains = net.earnings.enf - net.earnings.non.enf)

# plot per round

plot.cb.enf <- db.ind %>% 
  select(id, 
         performance, 
         framing,
         group_id, 
         round, 
         overextraction, 
         observer, 
         overext_observed, 
         report, punished, 
         round_profit, 
         group.id.fixed, 
         stage, 
         punished.na.to.zero, 
         report.na.to.zero, 
         sum.overextr, 
         sum.overextr.oth) %>% 
  mutate(
    # renamimng variables
    frame = ifelse(framing == 1, "CEAR", "pseudo-OA"),
    performance = ifelse(performance == 1, "High-performance", "Low-performance"),
    # not considering gains for being assigned an inspector
    profit.round = (100 + overextraction - (0.5 * sum.overextr.oth))* 10,
    profit.round = ifelse(punished.na.to.zero == 1, 0, profit.round),
    # subjects that were payed 250 in each round
    payed.inspector = ifelse(observer == 1 & overext_observed > 0, 1, 0),
    stage = ifelse(round > 10, "Peer-enforced", "Non-enforced")
  ) %>% 
  group_by(round, 
           performance, 
           frame, 
           stage) %>% 
  summarise(
    n.payed.inspectors = sum(payed.inspector),
    total.profit = sum(profit.round),
    total.cost  = ifelse(is.na(n.payed.inspectors), 0, n.payed.inspectors*250),
    net.earnings = (total.profit - total.cost)
    #net.earnings = total.profit
  ) %>% 
  mutate(round = ifelse(round > 10, round -10, round)) %>% 
  select(-c(n.payed.inspectors, total.profit, total.cost)) %>% 
  spread(stage, net.earnings) %>% 
  rename(net.earnings.enf = "Peer-enforced", 
         net.earnings.non.enf = "Non-enforced") %>% 
  mutate(net.gains = net.earnings.enf - net.earnings.non.enf,
         condition = paste(performance, frame)) %>% 
  ggplot(aes(x = as.factor(round), y = net.gains, fill= frame))+
  scale_fill_manual(values = c("royalblue3", "red1"), labels = c("CEAR (Loco)", "pseudo OA (Hake)"))+
  geom_bar(stat= 'identity') +
  facet_wrap(~ condition) +
  ylab("Net earnings (CLP)")+
  xlab("Round")+
  theme_classic()

plot.cb.enf

ggsave("FigS2_rev.jpg", plot = plot.cb.enf, device = "jpg", path = here::here("figures"), scale = 1, width = 16, height = 12, units = "cm", dpi = 600, limitsize = TRUE)
```


